---
title: "Hypo_Portfolio"
author: "Eric Hailer"
date: "11/11/2020"
output: html_document
---

### Load Packages

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(tidyquant)
library(gganimate)
library(quantmod)
library(timetk)
library(tibbletime)
library(scales)
library(highcharter)
library(broom)
library(PerformanceAnalytics)
```

### Data Import


Pull stock returns from Yahoo Finance using the "tidyquant" packages.  The Quantmod package pulls stock retruns in an XTS format while tidyquant pulls the same stock data into a "tidy" format.  In some instances one is "better" than the other when ivolving different packages for visualizations, analysis, statistcs, however the data is ubiquitous.

```{r}

daily_prices <- c("AAPL", "GOOG", "NFLX") %>%
    tq_get(get  = "stock.prices",
           from = "1990-11-01",
           to   = "2020-11-01")

head(daily_prices)
```

The benefit of the Tidyquant package is the "tidy" output of the pulled Yahoo Finance daily price data. Tidy data is a standard way of mapping the meaning of a dataset to its structure. A dataset is messy or tidy depending on how rows, columns and tables are matched up with observations, variables and types. In tidy data:

1) Each variable forms a column.

2) Each observation forms a row.

3) Each type of observational unit forms a table. 

This allows simple and efficient analsysis on large datasets

Lets show some simple data vizualiations of the pulled prices


```{r}
daily_prices %>%
  filter(symbol == "AAPL") %>%
  hchart(.,
        type = "line",
        hcaes(x = date,
              y = adjusted)) %>%
  hc_title(text = "AAPL Daily Price (Adjusted)")
  

```

Since all we have right now are prices, let's add a column for monthly returns  

```{r}

monthly_returns <- c("AAPL", "GOOG", "NFLX", "SPY") %>%
  tq_get(get = "stock.prices",
         from = "2000-01-01",
         to = "2020-11-01") %>%
  group_by(symbol) %>%
  tq_transmute(select = adjusted,
               mutate_fun = periodReturn,
               period = "monthly") %>%
  mutate(
    monthly_return = round(monthly.returns * 100, digits = 2))

head(monthly_returns)

```


let's set up the same chart but as a bar chart and see if that's cleaner. Let's also change returns from monthly to yearly.


```{r}

yearly_returns <- c("AAPL", "GOOG", "NFLX", "SPY") %>%
  tq_get(get = "stock.prices",
         from = "2000-01-01",
         to = "2020-11-01") %>%
  group_by(symbol) %>%
  tq_transmute(select = adjusted,
               mutate_fun = periodReturn,
               period = "yearly") %>%
  mutate(
    pct_return = round(yearly.returns * 100, digits = 2
  )) #this line crates a column that converts the returns into a percentage and rounds 

#Lets plot the yearly returns

yearly_returns %>%
    hchart(.,
         type = "scatter",
         hcaes(x = date,
               y = pct_return,
               group = symbol)) %>%
  hc_yAxis(opposite = TRUE,
           labels = list(format = "{value}%")) %>%
  hc_tooltip(pointFormat = '{point.x:%Y-%m-%d}
                            {point.y:4f}%')


```

Not the best visualization, but with replacing just one line of code we can easily tranform the above into a line chart for better viewing

```{r}

yearly_returns %>%
    hchart(.,
         type = "line",
         hcaes(x = date,
               y = pct_return,
               group = symbol)) %>%
  hc_yAxis(opposite = TRUE,
           labels = list(format = "{value}%")) %>%
  hc_tooltip(pointFormat = '{point.x:%Y-%m-%d}
                            {point.y:4f}%')



```


Lets see how this looks when we animate it 

```{r}
yearly_returns %>%
  ggplot(aes(x = date, y = pct_return, color = symbol)) +
  geom_line(size = .75) +
  geom_point() +
  ggtitle("Yearly Returns",
          subtitle = "2000-01-01 to 2020-11-01") +
  ylab("Return") +
  xlab("Date") +
  transition_reveal(date)

```
Why tidy data? We can easily perform iterative analysis on our data set


What was the best performing year of each stock over the last decade?

```{r}

yearly_returns %>%
  group_by(symbol) %>%
  arrange(desc(pct_return)) %>%
  slice_head() %>%
  select(symbol, date, pct_return)

```

Efficient statistical anylsis 


```{r}

yearly_returns %>%
  select(symbol, date, pct_return) %>%
  group_by(symbol) %>%
  summarise(
    mean = mean(pct_return),
    sd = sd(pct_return),
    median = median(pct_return))
```
